Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-24 journal paper/content/related_work.tex
A few more edits.
edits to related work

\asedit{\xhdr{Choice models.}
Relaxed choice models} similar to ours are found in several notable lines of work. First, ``random agents" (a.k.a. noise traders) can side-step the ``no-trade theorem'' \citep{Milgrom-Stokey-82}, a famous impossibility result in financial economics. Second, the \SoftMaxRandom model is closely related to the literature on \emph{product differentiation}, starting from \cite{Hotelling-29}, see \cite{Perloff-Salop-85} for a notable later paper. Third, a large literature on non-existence of equilibria due to small deviations (starting with \cite{Rothschild-Stiglitz-76} in the context of health insurance markets) is related to the corresponding non-existence result for \HardMaxRandom. Notable recent papers \citep{Veiga-Weyl-16,Azevedo-Gottlieb-17} emphasize the distinction between \HardMax and versions of \SoftMaxRandom in this context.
\asdelete{While agents' rationality and severity of competition are often modeled separately in the literature, it is not unusual to have them modeled with the same ``knob" \cite[\eg][]{Gabaix-16}.}

>>>>

\asedit{\xhdr{Choice models.}}
\gaedit{Relaxed choice models similar to ours are found in several notable lines of work. First, ``random agents" (a.k.a. noise traders) can side-step the ``no-trade theorem'' \citep{Milgrom-Stokey-82}, a famous impossibility result in financial economics, and play a similar role in our model as we move from \HardMax to \HardMaxRandom.  Furthermore, a large literature on non-existence of equilibria due to small deviations (starting with \cite{Rothschild-Stiglitz-76} in the context of health insurance markets) is related to the corresponding non-existence result for \HardMaxRandom. Second, the stochastic choice rules we consider have been widely utilized across economics. For instance, \SoftMaxRandom includes the standard logit choice rule, which has been widely used throughout economics with strong micro-foundations \citep{luce1959choice, mcfadden1974measurement, matvejka2015rational}, as a special case. The functional form for the \SoftMaxRandom model is similar to that in standard horizontal production differentiation models (e.g. \cite{Hotelling-29, Perloff-Salop-85}). \cite{Veiga-Weyl-16,Azevedo-Gottlieb-17} emphasize the distinction between \HardMax and versions of \SoftMaxRandom.}
\asdelete{While agents' rationality and severity of competition are often modeled separately in the literature, it is not unusual to have them modeled with the same ``knob" \cite[\eg][]{Gabaix-16}.}
